Motional Quantum Ground-State Cooing of a Single Sodium Atom

### 2017-06-04 paper.tex
Expand conclusion and abstract

\begin{abstract}
  % (add a general sentence on the importance or motivation of the work)
  % Controlling quantum motion of...
  % (state the challenge),
  % (Give the result and brief solutions),
  % (outlook)
  We report Raman sideband cooling of a single neutral sodium atom to its three-dimensional
  motional ground state in an optical tweezer.
  Despite having a very large Lamb-Dicke parameter, high initial temperature and
  large differential AC Stark shift in the excited state,
  we observe a ground state preparation fidelity of $XX\%$ after a few hundred ms of cooling.
  We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable to
  systems where tight confinement or low initial cooling is hard to achieve.  The is particularly relevant for systems which are challenging to laser-cool, such as molecules and exotic atoms, and opens up a new approach for further cooling of these systems.
\end{abstract}

@@

Single neutral atoms trapped in optical tweezers provide a promising system
for various applications including quantum information, quantum chemistry
and quantum simulation of many-body systems.
Long-range interactions between the sites can be achieved by using Rydberg atoms, polar molecules, or dipolar atoms.
Polar molecules offer the additional advantage of a high degree of tunability, including the shape, range, and strength of the interaction.
Arrays of optical tweezers offer the ability to move, detect, and manipulate individual sites, andcan be used to prepare complex interacting systems
with high fidelity.
In order to achieve long coherence time and full quantum control of the system needed for
these applications,
it is usually necessary to control the thermal motion of the atoms by cooling to the
three dimensional motional ground state in the optical tweezer,
which has already been demonstrated with heavy alkali atoms including rubidium and cesium.
However, some of the important properties of previous experiments,
for example low initial temperature and small Lamb-Dicke parameter,
may not be easily achievable for other systems, such as directly laser-cooled polar molecules, or atoms with challenging sub-Doppler cooling such as Na, K, and Li.
To extend the versatility of this approach, we must be able to apply it in a more general case. 
In this letter, we cool single sodium atoms
trapped in optical tweezers to the motional ground state with Raman sideband cooling.
Despite having a large Lamb-Dicke parameter and high initial temperature, we are able to achieve a ground state probability of $XX\%$
by utilizing several new cooling techniques and a carefully optimized cooling sequence.

@@

Combining the axial and radial cooling results, we have achieved a ground state probability of
$....$. We believe this is currently limited by off-resonant scattering from the Raman beams
and the resonance shift caused by magnetic field fluctuation.
Improvements on these should improve the cooling performance even further.

>>>>

\begin{abstract}
  Single neutral atom trapped in optical tweezer is a promising system for various applications
  in quantum information and simulation.
  The control of the motional states for such a system is crucial
  for exploiting its full potential.
  We report Raman sideband cooling of a single sodium atom to its three-dimensional
  motional ground state in an optical tweezer.
  Despite having a very large Lamb-Dicke parameter, high initial temperature and
  large differential AC Stark shift in the excited state,
  we achieved a ground state preparation fidelity of $XX\%$ after a few hundred ms of cooling
  by using a few new cooling techniques including addressing high order Raman sideband.
  We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable to
  systems where tight confinement or low initial cooling is hard to achieve.
  The is particularly relevant for systems which are challenging to laser-cool,
  such as molecules and exotic atoms, and opens up a new approach for further cooling
  of these systems.
\end{abstract}

@@

Single neutral atoms trapped in optical tweezers provide a promising system
for various applications including quantum information, quantum chemistry
and quantum simulation of many-body systems.
Long-range interactions between the sites can be achieved by using Rydberg atoms,
polar molecules, or dipolar atoms.
Polar molecules offer the additional advantage of a high degree of tunability,
including the shape, range, and strength of the interaction.
Arrays of optical tweezers offer the ability to move, detect, and manipulate individual sites,
and can be used to prepare complex interacting systems with high fidelity.
In order to achieve long coherence time and full quantum control of the system needed for
these applications,
it is usually necessary to control the thermal motion of the atoms by cooling to the
three dimensional motional ground state in the optical tweezer,
which has already been demonstrated with heavy alkali atoms including rubidium and cesium.
However, some of the important properties of previous experiments,
for example low initial temperature and small Lamb-Dicke parameter,
may not be easily achievable for other systems, such as directly laser-cooled polar molecules,
or atoms with challenging sub-Doppler cooling such as Na, K, and Li.
To extend the versatility of this approach, we must be able to apply it in a more general case.
In this letter, we cool single sodium atoms
trapped in optical tweezers to the motional ground state with Raman sideband cooling.
Despite having a large Lamb-Dicke parameter and high initial temperature, we are able to achieve a ground state probability of $XX\%$
by utilizing several new cooling techniques and a carefully optimized cooling sequence.

@@

Combining the axial and radial cooling results,
we have achieved a ground state probability of $....$.
We believe this is currently limited by off-resonant scattering from the Raman beams
and the resonance shift caused by magnetic field fluctuation.
Improvements on these should improve the cooling performance even further.
We have shown that despite the difficulty in cooling sodium atoms,
it is possible to achieve reliable three dimensional cooling with significant ground state
probability using new cooling techniques and a optimized cooling sequence.
This opens up the possibility of cooling a large variety of systems to their motional ground
state using Raman sideband cooling that is challenging to laser cool
including molecules and exotic atoms.
